Streaming Fact Extraction for Wikipedia Entities at Web-Scale

### 2014-01-29 paper/flairs27_AuthorKit/paper.tex

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algorithmic} 
%\usepackage{cite }
%\usepackage{natbib}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Streaming Fact Extraction for Wikipedia Entities at Web-Scale)
/Author (Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang, Milenko Petrovic)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Streaming Fact Extraction for Wikipedia Entities at Web-Scale}
\author{Morteza Shahriari Nia$*$, Christan Grant$*$, \\
\bf \large Yang Peng\footnote{All authors contributed equally.}, Daisy Zhe Wang\\
Data Science Research Lab\\
University of Florida\\\
Gainesville, Florida 32611\\
\And Milenko Petrovic\\
Institute for Human and Machine Cognition\\ 15 SE Osceola Ave \\\ Ocala, Florida 34471
}

@@

\begin{figure}
\hspace{-10mm}
  \centering
%  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
  \includegraphics[width=8.5cm]{./images/System_Diagram_with_model_Vertical-crop.pdf}
% http://convert.neevia.com/pdfconvert/
  %\vspace*{-.1in} 
  \caption{System Architecture.
  Components are logical groups noted with dotted boxes.}
  \label{fig:system}
  %\vspace*{-.2in}
\end{figure}

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algorithmic} 
%\usepackage{cite }
%\usepackage{natbib}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Streaming Fact Extraction for Wikipedia Entities at Web-Scale)
/Author (Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang, Milenko Petrovic)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Streaming Fact Extraction for Wikipedia Entities at Web-Scale}
\author{Morteza Shahriari Nia$^*$, Christan Grant$^*$, \\
\bf \large Yang Peng\thanks{All authors contributed equally.}, Daisy Zhe Wang\\
Data Science Research Lab\\
University of Florida\\\
Gainesville, Florida 32611\\
\And Milenko Petrovic\\
Institute for Human and Machine Cognition\\ 15 SE Osceola Ave \\\ Ocala, Florida 34471
}

@@

\begin{figure}
%\hspace{-10mm}
  \centering
%  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
  \includegraphics[width=8.5cm]{./images/System_Diagram_with_model_Vertical-crop.pdf}
% http://convert.neevia.com/pdfconvert/
  %\vspace*{-.1in} 
  \caption{System Architecture.
  Components are logical groups noted with dotted boxes.}
  \label{fig:system}
  %\vspace*{-.2in}
\end{figure}
